---
title: "MBTI personality based on Reddit machine learning project "
author: "PENGYU YANG"
output: pdf_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

<h4>As the size of dataset is big, so pls make sure clearing memory in time </h4> 
<h4>Also please make sure all of the packages have been updated </h4。


```{r}

memory.limit(150000)

```

```{r pressure, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(tidytext)
library(tidyr)
library(tidymodels) # tidymodeling contains recipe package
library(readr)
library(keras)
library(stringr)
library(randomForest)
library(hunspell)
library(wordcloud)
library(forcats)
library(SnowballC)
library(reshape2)
library(Rcpp)
library(MASS) # for LDA C reates problems for select
library(janitor) # clean up variable names
library(Rtsne) # for tsne
library(embed) # for umap
library(irlba) # svd decomp
library(correlationfunnel)
library(ranger)
library(BKPC) # for marginal relevance  and kernels

```



```{r}

mbti9k_comments <- read_csv("mbti9k_comments.csv", 
    col_types = cols(comments_num = col_skip(), 
        mbti_subreddits_commented = col_skip(), 
        subreddits_commented = col_skip(), 
        wc = col_skip()))

mbti9k_comments$type = as.factor(mbti9k_comments$type)

```



```{r}
#tidy comment one token per row

tidy_comments <-mbti9k_comments %>% unnest_tokens(word,comment) 

head(tidy_comments)

rm(mbti9k_comments)
gc()

#saveRDS(tidy_comments,file = "tidy_comments.rds")
tidy_comments <-readRDS(file = "tidy_comments.rds")
```



```{r}
# remove stop words and list the frequency of the rest words

tidy_no_stop   <- tidy_comments %>% anti_join(get_stopwords())

rm(tidy_comments)

gc()
```



```{r}

## Remove or replace number by words and remove website etc

tidy_no_stop <- tidy_no_stop[-grep("http", tidy_no_stop$word), ]
gc()

tidy_no_stop <- tidy_no_stop[-grep("www.", tidy_no_stop$word), ]
gc()

tidy_no_stop <- tidy_no_stop[-grep(".com", tidy_no_stop$word), ]
gc()

tidy_no_stop <- tidy_no_stop[-grep("here_it_is", tidy_no_stop$word), ]
gc()

tidy_no_stop <- tidy_no_stop[!str_detect(tidy_no_stop$word,"[^\x01-\x7F]"),]
gc()

tidy_no_stop <- tidy_no_stop[!str_detect(tidy_no_stop$word,"[0-9*]"),]
gc()

saveRDS(tidy_no_stop, file = "tidy_com_nostop.rds")

```



Find misspelled words and remove them using a costom dictionary. Tidy up memory.

```{r}
## find the misspelled words
tidy_no_stop$word <- as.character(tidy_no_stop$word)
tidy_no_stop$type <- as.factor(tidy_no_stop$type)

bad.words <- hunspell(tidy_no_stop$word)
bad.words1 <- unlist(bad.words)


# custom stop words
custom_stop_words <- bind_rows(stop_words, data_frame(word = bad.words1,
           lexicon = "custom"))

```


```{r}
custom_stop_words <- custom_stop_words[custom_stop_words$word!="like",]
custom_stop_words <- custom_stop_words[custom_stop_words$word!="mbti",]
custom_stop_words <- custom_stop_words[custom_stop_words$word!="atm",]
custom_stop_words <- custom_stop_words[custom_stop_words$word!="btw",]
custom_stop_words <- custom_stop_words[custom_stop_words$word!="bff",]
custom_stop_words <- custom_stop_words[custom_stop_words$word!="lol",]
custom_stop_words <- custom_stop_words[custom_stop_words$word!="booooring",]
custom_stop_words <- custom_stop_words[custom_stop_words$word!="overdetermined",]
custom_stop_words <- custom_stop_words[custom_stop_words$word!="xkcd",]
custom_stop_words <- custom_stop_words[custom_stop_words$word!="hyperfocus",]

tidy_comments <- tidy_comments %>% anti_join(custom_stop_words)
```


```{r}

# Restore the object
tidy_no_stop <- readRDS(file = "tidy_com_nostop.rds")

```



<h2>Top words used in total</h2>

```{r}

tidy_comments_visual <-tidy_no_stop %>%
                          count(word,sort = TRUE) %>%
                          mutate(word = reorder(word,n))

# visualizing the top words  
ggplot(data=tidy_comments_visual[1:20,],aes(x = word, y = n))+
  geom_col()+ 
  coord_flip()

```

```{r}
#saveRDS(tidy_comments_visual, file = "tidy_com_visual.rds")
tidy_comments_visual <- readRDS(file = "tidy_com_visual.rds")

```




<h3>word cloud </h3> 
```{r}
# word cloud

tidy_comments_visual %>% 
  mutate(word = reorder(word,n))%>% 
  with(wordcloud(word, n, random.order = FALSE, max.words = 100, colors = "#F29545"))

```




```{r}

# high frequencies words used in each type

tidy_comments_bytype <- tidy_no_stop %>% 
                      count(type,word,sort = TRUE) %>% 
                      group_by(type) %>%
                      arrange(type) 

tidy_comments_bytype$type <- as.factor(tidy_comments_bytype$type)


# save rds
saveRDS(tidy_comments_bytype, file = "tidy_com_bytype.rds")
tidy_comments_bytype <- readRDS(file = "tidy_com_bytype.rds")



# the percentage of words used in each type (filter the words used over 500 times)

new_tidy_comments_bytype <- tidy_comments_bytype %>% filter( n>500) %>% 
                        group_by(type) %>% 
                        mutate(total = sum(n), percent = n/total)
```


```{r}

# top 15 high frequencies words used in each type
new_tidy_comments_bytype %>%
      top_n(n, n = 15) %>% #slice_max
      ungroup() %>% 
      ggplot(aes(n, fct_reorder(word, n), fill = type)) +
      geom_col(show.legend = FALSE) +
      facet_wrap(~type, ncol = 4, scales = "free") +
      labs(x = "n", y = NULL)

```


```{r}
# high frequencies words used in each type
gc()
tidy_comments_byauthor <- tidy_no_stop %>% 
                      count(author,word,sort = TRUE) %>% 
                      group_by(author) %>%
                      arrange(author) 

tidy_comments_byauthor$author <- as.factor(tidy_comments_byauthor$author)


# save author rds
#saveRDS(tidy_comments_byauthor, file = "tidy_com_byauthor.rds")
tidy_comments_byauthor <- readRDS(file = "tidy_com_byauthor.rds")



```

<h1>TF-IDF</h1>
```{r}
#tf-idf

total_words <- tidy_comments_bytype %>%
  group_by(type) %>% 
  summarize(total_in_type = sum(n))


#how many words 

comment_words <- left_join(tidy_comments_bytype, total_words)


comment_tf_idf <- comment_words %>%
  bind_tf_idf(word, type, n)


comment_tf_idf  %>%
  dplyr::select(-total_in_type) %>%
  arrange(desc(tf_idf))

comment_tf_idf %>%
  group_by(type) %>%
  top_n(tf_idf, n = 15) %>% #slice_max
  ungroup() %>%
  ggplot(aes(y=tf_idf, x=fct_reorder(word, tf_idf), fill = type)) +
  geom_col(show.legend = FALSE) +
  coord_flip()+
  facet_wrap(~type, ncol = 4, scales = "free") +
  labs(x = "tf-idf", y = NULL)


rm(comment_words)


```

```{r}
# saveRDS(comment_tf_idf, "comment_tf_idf.rds")
comment_tf_idf <- readRDS(file = "comment_tf_idf.rds")

```


TF - IDF by author (for analysis):

```{r}
# this step has been done above
#tidy_comments_byauthor <- tidy_no_stop %>% 
#                      count(author,word,sort = TRUE) %>% 
#                      group_by(author) %>%
#                      arrange(author) 


total_words <- tidy_comments_byauthor %>% 
  group_by(author) %>% 
  summarize(total = sum(n))

tidy_author_words <- left_join(tidy_comments_byauthor, total_words)


```

```{r}

# words at appear in at least 8000 different comments
words_8000 <- tidy_comments_byauthor %>%
  group_by(word) %>%
  summarise(n = n()) %>%
  filter(n >= 8000) %>%
  dplyr::select(word)


#saveRDS(words_5000, file = "words_5000.rds")
#saveRDS(words_8000, file = "words_8000.rds")

words_5000 <- readRDS(file = "words_5000.rds")
words_8000 <- readRDS(file = "words_8000.rds")


tidy_author_words2 <-  tidy_author_words %>% right_join(words_8000, by = "word")



```



Redo tf-idf (author)
```{r}

author_tf_idf <- tidy_author_words2 %>%
  bind_tf_idf(word, author, n)

#saveRDS(author_tf_idf, file = "author_tf_idf.rds")

author_tf_idf  %>%
  dplyr::select(-total) %>%
  arrange(tf_idf)


```

Get the dataset in tidy format (sparse here).
```{r}
library(tm)

xt <- author_tf_idf %>%
      cast_dtm(author, word, tf_idf)

```


Break out of sparse format
```{r}
xt2 <- xt %>% as.matrix() %>% as.data.frame()
xt2 <- xt2 %>% mutate(author = dimnames(xt)[[1]])
xt2[1:5, 1:5]

rm(xt)

```



<h2>Sentiments anaylysis</h2>
```{r}
#Sentiment lexicons
get_sentiments("bing")

```


```{r message=FALSE, warning=FALSE}

# implement sentiment analysis(qingxu fenxi) in comments with bing sentiment lexicons(qingxu cihui)

comment_sentiment <-tidy_comments_bytype %>%
                    inner_join(get_sentiments('bing'))

# find of how many positive and negative words each type of personality has
comment_sentiment_count <-comment_sentiment %>%
                    count(type,sentiment) %>% view()

```



```{r}

#find the percentage of negative words in each personality type

comment_sentiment_count_new <- comment_sentiment_count %>% 
  group_by(type) %>%
  mutate(total = sum(n), percent =round( n/total *100, 5))

comment_sentiment_count_new$sentiment <- as.factor(comment_sentiment_count_new$sentiment)

comment_sentiment_count_new %>%
  ggplot(aes(x = type, y = percent,fill = sentiment))+ geom_col()+
  ggtitle('Sentiments percentage (By type)')


rm(comment_sentiment)
```

```{r}
#sentiments by author

comment_sentiment2 <- tidy_comments_byauthor %>%
                    inner_join(get_sentiments('bing'))


author_comment_sentiment <- comment_sentiment2 %>% count(author,sentiment) %>% 
  group_by(author) %>%
  mutate(total = sum(n), percent = round(n/total * 100,5)) %>%
  # filter the results for only negative sentiment in each type
  filter(sentiment == 'negative') 
  
author_comment_sentiment %>% arrange(desc(percent))

rm(comment_sentiment2)

```

```{r}

meta <- tidy_no_stop %>%  dplyr::select(c("author", "type")) 

meta <- meta %>% group_by(author,type) %>% count(author,type) %>% dplyr::select(c("author", "type"))

#saveRDS(meta, file = "meta.rds")
gc()

author_comment_sentiment<- author_comment_sentiment %>%
  left_join(meta, by = "author")

#saveRDS(author_comment_sentiment, file = "author_comment_sentiment.rds")
author_comment_sentiment <- readRDS(file = "author_comment_sentiment.rds")

author_comment_sentiment %>% ggplot(aes(x= type, y = percent)) +geom_boxplot()+
  ggtitle("Negative sentiments by type & author")


rm(tidy_no_stop)
gc()
```

Sentiments in word cloud
```{r warning=FALSE}

tidy_comments_visual1 <- tidy_comments_visual %>% 
             inner_join(get_sentiments("bing"))

tidy_comments_visual1 $sentiment <- as.factor(tidy_comments_visual1$sentiment)

tidy_comments_visual1 %>% acast(word~ sentiment, value.var = "n",fill = 0) %>%
  comparison.cloud(colors = c("#F8766D", "#00BFC4"),max.words = 100, title.size =2,
                   title.colors = 'white',title.bg.colors = 'lightpink' )

```

clean memory
```{r}
rm(tidy_comments_visual)
gc()

```

Save version with sentiments.
```{r}

xt3 <- xt2 %>% dplyr::select(-author) #remove author column

xt4 <- xt3[rowSums(xt3)>0,]
xt4 <- xt2[rownames(xt4),]

xt5 <- xt4 %>%
  left_join(meta[!duplicated(meta$author), ], by = "author")


xt6 <- xt5 %>% 
  left_join(author_comment_sentiment, by = "author")

xt6 <- xt6  %>% dplyr::select(-c(sentiment,n))
xt6 <- xt6  %>% na.omit()
               

xt6  <- xt6 %>% rename(type = type.x, mbtitype = type.y)
names(xt6)

saveRDS(xt6,"xt6.rds")

rm(xt3)
rm(xt4)
rm(xt5)
rm(tidy_author_words)
rm(tidy_author_words2)

```


Exploratory analysis

Read in the data

```{r}
set.seed(12345)

xt6 <- readRDS("subtract_type.rds")

xt6 <- readRDS("xt6.rds")

```


To simplify work with only the introverts/extroverts.
```{r}
xt6 <- xt6 %>% mutate(labelmbtiintrovert = substring(mbtitype, 1, 1))
xt6 <- xt6 %>% mutate(labelmbtisensing = substring(mbtitype, 2, 2))
xt6 <- xt6 %>% mutate(labelmbtithinking = substring(mbtitype, 3, 3))
xt6 <- xt6 %>% mutate(labelmbtijudging = substring(mbtitype, 4, 4))
```


Rename variables
```{r}
xt6 <- xt6 %>% rename(percentnegative = percent)
xt6 <- xt6 %>% rename(labelmbtitype = mbtitype)
xt6 <- janitor::clean_names(xt6)
```

Correlation funnel plot
```{r}
xt6_bin <- xt6 %>%
  binarize(n_bins = 5, thresh_infreq = 0.001, name_infreq = "OTHER", one_hot = TRUE)


xt6_corr <- xt6_bin%>% 
  rename(mbtiintrovert__e = labelmbtiintrovert__e) %>% 
  dplyr::select(!starts_with("label")) %>% 
  correlate(mbtiintrovert__e)


xt6_corr[1:30,] %>%
  plot_correlation_funnel()

```


```{r}
xt6_corr <- xt6_bin %>% 
  rename(mbtisensing__n = labelmbtisensing__n) %>% 
  dplyr::select(!starts_with("label")) %>% 
  correlate(mbtisensing__n)

xt6_corr[1:30,] %>%
  plot_correlation_funnel()
```



```{r}
xt6_corr <- xt6_bin %>% 
  rename(thinking__f = labelmbtithinking__f) %>% 
  dplyr::select(!starts_with("label")) %>% 
  correlate(thinking__f)

xt6_corr[1:30,] %>%
  plot_correlation_funnel()
```


```{r}
xt6_corr <- xt6_bin %>% rename(mbtijudging__j = labelmbtijudging__j) %>% dplyr::select(!starts_with("label")) %>% correlate(mbtijudging__j)

xt6_corr[1:30,] %>%
  plot_correlation_funnel()
```



<h1>Random sampling</h1>
Scale and center data
```{r warning=FALSE}
me <- apply(xt6 %>% dplyr::select(!starts_with("label")), 2, mean)
sd <- apply(xt6 %>% dplyr::select(!starts_with("label")), 2, sd)

x.sc <- sweep(xt6 %>% dplyr::select(!starts_with("label")), 2, me, "-")
x.sc <- sweep(x.sc , 2, sd, "/")
x.sc <- x.sc  %>% bind_cols(xt6 %>% dplyr::select(starts_with("label")))
xt6 <- x.sc



```


```{r}
xt6  <- xt6 %>% arrange(labelmbtitype)

table(xt6$labelmbtitype)
```


```{r}
set.seed(2021)

trainIndex <- c(sample(table(xt6$labelmbtiintrovert)[1], 1000),               
                table(xt6$labelmbtiintrovert)[1] + 
                sample(table(xt6$labelmbtiintrovert)[2],5500))


table(xt6$labelmbtiintrovert)

```

```{r}
# Set training dataset and test dataset

data_df_train <- xt6[trainIndex, ] 
data_df_test <- xt6[-trainIndex, ]

```


<h1>Marginal relevance</h1>
```{r}
#find MR scores

dtf <-  data_df_train %>% rename(mbtitype = labelmbtiintrovert) %>% 
  dplyr::select(!starts_with("label")) %>% mutate(mbtitype = as.factor(mbtitype))


dtf <- dtf %>% dplyr::select(-c(author, type, total, percentnegative))

margRelv <- marginalRelevance(dtf %>% dplyr::select(!mbtitype),dtf$mbtitype)




mr <- t(margRelv$score) %>% as.tibble() %>% rename(value = V1)

mr <- mr %>% mutate(word = names(dtf %>%  dplyr::select(!mbtitype)))

mr <- mr %>% arrange(desc(value))
mr2 <- mr[1:25,]
mr2 %>%
  mutate(word = reorder(word,value)) %>% ggplot(aes(x = word, y = value))  + geom_point()  + coord_flip() + ggtitle("MR: introvert - extrovert")


```


<h1>Dimension reduction</h1>
<h2>PCA</h2>

```{r}

# choose numeric variables
data_df_train1 <- data_df_train %>% dplyr::select(-c(author, type, total, percentnegative))

pctext <- prcomp(data_df_train1 %>%  dplyr::select(!starts_with("label")),scale. = TRUE )

tidyPCA <- tibble(PC1 = pctext$x[,1], PC2 = pctext$x[,2], PC3 = pctext$x[,3])
tidyPCA <- tidyPCA %>% mutate(type = data_df_train$labelmbtitype, typei = data_df_train$labelmbtiintrovert, types = data_df_train$labelmbtisensing,
                              types = data_df_train$labelmbtisensing,  typet = data_df_train$labelmbtithinking,  typej = data_df_train$labelmbtijudging)

tidyPCA %>% ggplot(aes(PC1, PC2, col = type)) + geom_point()
```


```{r}

tidyPCA %>% ggplot(aes(PC1, PC2,col = typei)) + geom_point() + 
  scale_colour_manual( values = c("darkblue", "lightgreen"),name = "Type" ,
                       labels = c("Extrovert", "Introvert"))
  
  
```


```{r}
tidyPCA %>% ggplot(aes(PC1, PC2, col = types)) + geom_point() + 
  scale_colour_manual( values = c("aquamarine2", "lightcoral"),
                       name = "Type",labels = c("Intuitive", "Sensor"))
```


```{r}
tidyPCA %>% ggplot(aes(PC1, PC2, col = typet)) + geom_point()+ 
  scale_colour_manual( values = c("indianred1", "mediumpurple1"),name = "Type",
                       labels = c("Feeler", "Thinker"))
```


```{r}
tidyPCA %>% ggplot(aes(PC1, PC2, col = typej)) + geom_point() + 
  scale_colour_manual( values = c("pink1", "steelblue2"),name = "Type",
                       labels = c("Judger", "Perceiver"))
```

----------------------- Density-----------------------
```{r}
tidyPCA %>% ggplot(aes(PC2, fill = typet)) +
  geom_density(alpha = 0.7) +
  scale_fill_manual( values = c("indianred1", "mediumpurple1"),name = "Type",
                     labels = c("Feeler", "Thinker"))

```

```{r}
tidyPCA %>% ggplot(aes(PC2, fill = typei)) +
  geom_density(alpha = 0.7) +
  scale_fill_manual( values = c("darkblue", "lightgreen"),name = "Type",
                     labels = c("Extrovert", "Introvert"))
```


```{r}
tidyPCA %>% ggplot(aes(PC2, fill = types)) +
  geom_density(alpha = 0.7) +
  scale_fill_manual( values = c("aquamarine2", "lightcoral"),name = "Type",
                     labels = c("Intuitive", "Sensor"))
```

```{r}
tidyPCA %>% ggplot(aes(PC2, fill = typej)) +
  geom_density(alpha = 0.7) +
  scale_fill_manual( values = c("pink1", "steelblue2"),name = "Type",
                     labels = c("Judger", "Perceiver"))
```




```{r}

pcwords <- prcomp(data_df_train[ , 1:97] %>% t(), scale. = TRUE )

# biplot(pcwords)

tidyPCA <- tibble(PC1 = pcwords$x[,1], PC3 = pcwords$x[,3], PC2 = pcwords$x[,2],  words = names(data_df_train)[1:97])

tidyPCA %>% ggplot(aes(PC2, PC3))+ geom_text(aes(label = words))
```


```{r}
tidyPCA %>% ggplot(aes(PC3, PC2))+ geom_text(aes(label = words))
```


```{r}
library(dendextend)


# clustering the columns (variables) rather than observations
D2 <- as.matrix(1-abs(cor(data_df_train[ , 1:97])))

# image(D2)


h2<- hclust(as.dist(D2), method = "ward.D2")
dnew <- as.dendrogram(h2)



d2 <- color_branches(dnew,k=15, col = 2:16) 


plot(d2)


labl.cols <- cutree(d2,15) # 15 variables

labl.cols[labl.cols==1]
```


```{r}
labl.cols[labl.cols==2]
```

```{r}
labl.cols[labl.cols==4]
```


```{r}
labl.cols[labl.cols==5]
```


```{r}
labl.cols[labl.cols==6]
```


```{r}
labl.cols[labl.cols==7]
```


```{r}
labl.cols[labl.cols==8]
```


```{r}
labl.cols[labl.cols==9]
```


```{r}
labl.cols[labl.cols==10]
```

```{r}
labl.cols[labl.cols==11]
```


```{r}
labl.cols[labl.cols==12]
```

```{r}
labl.cols[labl.cols==13]
```


```{r}
labl.cols[labl.cols==14]
```


```{r}
labl.cols[labl.cols==15]
```


<h1>Tidy PCA</h1>

```{r}

pca_rec <- recipe(~., data = data_df_train1 %>% rename(mbtitype = labelmbtitype) %>%  
  dplyr::select(!starts_with("label"))) %>%
  update_role(mbtitype, new_role = "id") %>%
  step_normalize(all_predictors()) %>%
  step_pca(all_predictors())

pca_prep <- prep(pca_rec)

tidied_pca <- tidy(pca_prep, 2)


tidied_pca %>%
  filter(component %in% paste0("PC", 1:4)) %>%
  group_by(component) %>%
  top_n(8, abs(value)) %>%
  ungroup() %>%
  mutate(terms = reorder_within(terms, abs(value), component)) %>%
  ggplot(aes(abs(value), terms, fill = value > 0)) +
  geom_col() +
  facet_wrap(~component, scales = "free_y") +
  scale_y_reordered() +
  labs(
    x = "Absolute value of contribution",
    y = NULL, fill = "Positive?"
  )


```



```{r}
juice(pca_prep) %>%
  ggplot(aes(PC2, PC3)) +
  geom_point(aes(color = mbtitype), alpha = 0.7, size = 2) +
  labs(color = NULL)
```

Tidy UMAP
```{r}
umap_rec <- recipe(~., data = data_df_train1 %>% rename(mbtitype = labelmbtiintrovert) %>%  
  dplyr::select(!starts_with("label"))) %>%
  update_role(mbtitype, new_role = "id") %>%
  step_normalize(all_predictors()) %>%
  step_umap(all_predictors())

umap_prep <- prep(umap_rec)

# umap_prep

juice(umap_prep) %>%
  ggplot(aes(umap_1, umap_2)) +
  geom_point(aes(color = mbtitype), alpha = 0.7, size = 2) +
  labs(color = NULL) +ggtitle("UMAP")
```

T-sne
With SVD decomp
```{r}
S <- irlba(t(data_df_train1 %>% dplyr::select(!starts_with("label"))), nv=20)
tsne <- Rtsne(S$v , k = 3)
tydy_tsne <- tsne$Y %>% as.tibble()
tidy_tsne <- tydy_tsne  %>% mutate(mbtitype  = data_df_train$labelmbtiintrovert)

#plot
tidy_tsne %>% ggplot(aes(V1, V2, col = mbtitype)) + 
  geom_point()+ 
  ggtitle("T-sne E/I") +
  scale_colour_manual(values= c("steelblue2","yellow2"), 
                      labels = c("Extrovert","Introvert"),name = "Type")


#SVD

tidy_svd %>% ggplot(aes(V3, V2, col = mbtitype)) + 
  geom_point()+
  ggtitle("SVD E/I") +
  scale_colour_manual(values= c("thistle2","turquoise"), 
                      labels = c("Extrovert","Introvert"),name = "Type")
```


<h1>Classification</h1>

<h2>Random forest </h2>
```{r}
dtf <- data_df_train1 %>% 
  rename(mbtitype = labelmbtiintrovert) %>% 
  dplyr::select(!starts_with("label")) %>% 
  mutate(mbtitype = as.factor(mbtitype))


data_df_test1 <- data_df_test %>% dplyr::select(-c(author, type, total, percentnegative)) 

dtf_test <- data_df_test1 %>% 
  rename(mbtitype = labelmbtiintrovert) %>% 
  dplyr::select(!starts_with("label")) %>% 
  mutate(mbtitype = as.factor(mbtitype))

modelfitrf2 <- ranger(mbtitype ~ ., importance = "impurity", data = dtf)

```



```{r}
pltdtf <- sort(modelfitrf2$variable.importance)[50:97] %>% as.tibble()
pltdtf <- pltdtf %>% mutate(word = names(sort(modelfitrf2$variable.importance)[50:97]))

pltdtf %>%
  mutate(word = reorder(word,value)) %>% ggplot(aes(x = word, y = value))  + geom_point()  + coord_flip() + ggtitle("RF: introvert - extrovert")
```


```{r}
pred.rf <- predict(modelfitrf2, dtf_test)
t <- table(dtf_test$mbtitype, pred.rf$predictions)
t
```



```{r}
sum(diag(t))/sum(t)

```


<h1>LDA</h1>
```{r}

dtf1 <- dtf[-c(1,2,4,10,18,20,26,33,47)]
# Error in lda.default(x, grouping, ...) :  variables  1  2  4 10 18 20 26 33 47 appear to be constant within groups

fit.lda1 <- lda(mbtitype ~. ,  data = dtf1)

predlda1 <- predict(fit.lda1, dtf_test)
t <- table(dtf_test$mbtitype, predlda1$posterior[,2] > 0.5)
t

```


```{r}
sum(diag(t))/sum(t)

```

```{r}
fit.lda1$svd
```


```{r}
fi <- predlda1$x
fi <- fi %>% as.tibble() %>% mutate(mbtitype = dtf_test$mbtitype)



fi %>% ggplot(aes(LD1, fill = mbtitype)) +
  geom_density(alpha = 0.5) + ggtitle("LDA E/I") + 
  scale_fill_manual( values = c("lightgreen","yellow"), name = 'Type',
                     labels = c("Extrovert","Introvert"))
```


```{r}
fi <- fit.lda1$scaling  %>% as.tibble() %>% mutate(word = rownames(fit.lda1$scaling) )%>% arrange(desc(abs(LD1)))

fi %>%
  mutate(word = reorder(word,abs(LD1)))%>%
  top_n(25, abs(LD1))  %>% ggplot(aes(x = word, y = LD1))  + geom_point()  + coord_flip() + ggtitle("LDA : introvert - extrovert")
```

